The Dynamics of Anthropomorphism in Human-Robot Interaction

### 2014-03-31 paper.tex
new bib item, minor refinements / typos first 5 pages

\title[The Dynamics of Anthropomorphism]{The Dynamics of Anthropomorphic Effects in Human-Robot Interaction}
\author[\firstAuthorLast ]{\Authors}
\address{}
\correspondance{}
\extraAuth{}
\topic{The Uncanny Valley Hypothesis and Beyond}% If your article is part of a Research Topic, please indicate here which.

@@

The Uncanny Valley hypothesis \citep{mori_uncanny_1970} proposes that human-like
designs of objects and non-human agents can evoke both positive and negative feelings 
of affinity in the human observer / user. Positive feelings reflect the experience of 
emotional engagement with and feelings of empathy for the non-human agent
\citep{cheetham_human_2011}. The positive effect of so-called
\textbf{anthropomorphic form} is exploited in the design of artificial agents
(\eg digital characters, robots) for several reasons. Amongst others,
anthropomorphic design should serve to evoke a positive valence as the Uncanny
Valley hypothesis suggests, which in turn should foster people's acceptance of
the artificial agent, and enable effective (human-like and especially
human-social) interaction.  However, at a certain point as the non-human agent
approaches but fails to closely resemble a human, the evoked valence in the
human user suddenly turns into a negative uncanny feeling of what
\cite{mori_uncanny_1970} describes as disgust and revulsion. This, in turn,
might lead to rejection of the non-human but human-like agent.  The Uncanny
Valley hypothesis predicts that with further increasing the human-likeness of
the non-human agent such that it appears so realistic that it is not
distinguishable from a human but perceived to be human, the effect is again a
positive one, reflecting feelings and engagement that are similar as those
evoked by a human-human interaction.  Of course, roboticists and developers try
to avoid ``falling'' into this Uncanny Valley with their human-like designs of
artificial agents. Consequently, there is a considerable research effort to
better understand the boundaries of anthropomorphic design and their effects
on the interaction and experience. To date, findings have been however
inconsistent \citep{cheetham_human_2011}.

Along this line, this article aims at fostering a better understanding of
\textbf{anthropomorphism} (noted \Ant in this paper) by considering the phenomenon
\textbf{as a whole}: robotics researchers often tend to believe that
anthropomorphism only describes a static set of human-like features of a robot
(like shape, speech capabilities, facial expressions, etc.). We refer to these
characteristics as the \emph{anthropomorphic design} of the
robot~\cite{fink_anthropomorphism_2012}. But \emph{anthropomorphism} in general
refers to the larger \emph{social phenomenon} that emerges from the (real or
imagined) \emph{interaction} between a robot and a
user~\citep{persson_anthropomorphism_2000}. According to~\cite{epley_when_2008},
this includes for instance emotional states, motivations, intentions
\emph{ascribed by the user} to the robot. As such, the dynamic and
socio-cognitive dimensions of anthropomorphism are essential to understand the
complex bonds that human users build with the robots.

@@

To support the reflection, it may be useful to consider a few experimental
results. We studied anthropomorphism effects in several short- and long-term
human-robot interaction studies that we carried out with embodied robots, both
in ecologically valid real-world environments and controlled lab settings. Those
experiments are presented in details in previously published
articles~\citep{fink_anthropomorphic_2012, fink_living_2013, fink2014which,
lemaignan2014dynamics}. We only highlight here a few qualitative results that
underline the complexity of the phenomenon.

\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.48\columnwidth}
                \includegraphics[width=\textwidth]{roomba-activities.png}
                \caption{Roomba activities}
                \label{fig:roomba-activities}
        \end{subfigure}%
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.48\columnwidth}
                \includegraphics[width=\textwidth]{roomba-perception.pdf}
                \caption{Roomba perception}
                \label{fig:roomba-perception}
        \end{subfigure}
    \caption{Usage and perception of the Roomba robot over a 6 months period.}
    \label{fig:roomba}
\end{figure}

Figures~\ref{fig:roomba-activities} and~\ref{fig:roomba-perception} give a first
perspective on how naive users interact and perceive robots over a long period
of time. Here, \emph{Roomba} vacuum cleaning robots were given to nine
households for a 6-months period. The aim was to explore how people use and
perceive the robot over time, and how they generally live with the Roomba in
their home. At various time points, users were asked to rate their perception of
different features of the robot on a 7-point rating scale. As
Figure~\ref{fig:roomba-perception} shows, some features remained stable over
time (\emph{ease of use} and \emph{fun}), and others decreased: the perceived
\emph{usefulness}, \emph{intelligence} and \emph{impact} on their household.
\emph{intelligence} and \emph{impact} reflect the cognitive engagement of the
user towards the machine: we can assume that one does not care to engage in a
(cognitive) interaction with an artifact perceived as non-intelligent and with
no impact on his/her life (and the level of activity pictured on
Figure~\ref{fig:roomba-activities} qualitatively confirms this intuition). Even
if one can argue that the Roomba is not designed to foster interaction, it
raises a first question: how to sustain engagement between a robot and a human
over a long period of time? And, as a pre-requisite to answer, do we actually
understand the psychological phenomenon, and can we effectively account for the
dynamics of these interactions?

Those questions are certainly not new, but paradoxically, while anthropomorphism
in robotics is a commonly discussed trait of human-robot interaction, it appears
that we lack formal grounds and models that would account for the long-term
dynamics of these interactions.

Figure~\ref{fig:qualitative-score} calls for other initial remarks. This diagram
comes from a (yet unpublished) study where 13 pairs of children (4-5 years old)
played for about 20 minutes a Domino game with a robot (the robot was tasked to
carry domino pieces from one child to the other, Figure~\ref{fig:ranger-expe}).
The $x$-axis represents the number of social interactions between the children
and the robot (like talking or showing objects), based on video annotations. On
the $y$-axis, we have a synthetic qualitative measurement of anthropomorphic
projections based on two questionnaires. The correlation between both these
values is significantly \emph{negative}: the more the children engaged into
interaction, the less prone to anthropomorphic projections they were. This
diagram also highlights an interesting cluster of children who did not interact
much with the robot, and still reported a strong anthropomorphic perception of
the robot.

\begin{figure}[h!]
        \centering
        \begin{subfigure}[t]{0.48\columnwidth}
                \centering
                \includegraphics[width=0.6\textwidth]{ranger}
                \caption{The \emph{Ranger} Domino study}
                \label{fig:ranger-expe}
        \end{subfigure}%
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[t]{0.48\columnwidth}
            \includegraphics[width=0.9\textwidth]{ranger-interactions-vs-qualitative-score}
            \caption{Qualitative level of anthropomorphic projections versus
            actual interactions with the robot}
            \label{fig:qualitative-score}
        \end{subfigure}
        \caption{Level of interaction with a semi-anthropomorphic robot is
        \emph{not} a predictor of anthropomorphic projections.}
    \label{fig:ranger}
\end{figure}

@@

These first remarks lead to the main question we attempt to address in this
article: how can we understand \emph{anthropomorphism} as a whole, and in such a
way that is support improved human-robot interactions?

Based on an extensive literature review~\citep{fink_anthropomorphism_2012},
several field and lab studies previously mentioned and insights from the
cognitive neurosciences, we propose to discuss anthropomorphism from three
complementary perspectives.

First, we would like to clarify what anthropomorphism actually \emph{means}:
besides the \emph{artifact-centered} understanding of anthropomorphism, it
seems important to explicit the human and social factors of anthropomorphism.

Then, we propose a model to understand how anthropomorphism evolves over time.
These dynamics are non-monotonic, and psychological factors like the
\emph{novelty effect} play here a key role.

@@

\paragraph{Two hypotheses} Our research question also translates to two
hypotheses, which structure the reflections of this article:

\item A person's tendency to anthropomorphize a robot
    is based on several factors, including (but not limited to) (1) the
    design of the robot, (2) the personal characteristics of the human user,
    and (3) the context and situation of use. For instance, a social context
    and purpose of the robot increase anthropomorphism: \textit{anthropomorphism
    as a multi-factor phenomenon}.

\item A person's tendency to anthropomorphize a robot
    evolves in a non-linear way over time and with growing experience that the
    person has with the robot. For instance, a more experienced user will
    perceive the robot as more familiar and predictable, and in turn
    anthropomorphizes the robot less: \textit{anthropomorphism as a dynamic
    phenomenon}.

@@

\begin{inparaenum}[\itshape 1)\upshape]

The remainder of this article is organized as follows.  First, in Section
\ref{sec:overview-studies}, we give a brief overview on the various studies that
we conducted to investigate anthropomorphism, namely \item the Roomba study,
\item the Forum study, \item the Ranger domino study. Next, Section
\ref{sec:anthropomorphism} aims to establish a common ground in the
understanding of anthropomorphism. We first explore an artifact-centered
perspective and briefly outline how the human-like design of agents can
encourage anthropomorphism.  Then, we explore a human-centered perspective
by integrating theories from cognitive science, developmental and social
psychology that serve to explain anthropomorphism. At the end of this
section we bring both perspectives together and interpret that
anthropomorphism is a multi-factor phenomenon.  Based on the two previous
sections, Section~\ref{sec:our-ideas} introduces an initial model of the
\textit{dynamics of anthropomorphism}. This model describes the variances
and dynamics of people's tendency to anthropomorphize an artificial agent,
such as a robot.  Then Section \ref{sec:cognition-neuroscience} presents a
cognitive and neuroscience perspective on anthropomorphism to consolidate
our considerations and the proposed model.  This is followed by a discussion
about the limitations of our approach (Section \ref{sec:discussion}) and the
existing and alternative ways to measure anthropomorphism in human-robot
interactions.  Finally, Section \ref{sec:conclusion} concludes this article
and offers starting points for further research on anthropomorphism and the
effect of the human-like design approach in robotics.

\end{inparaenum}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%		PART 1: WHAT OTHERS DID AND WE ALREADY KNOW ABOUT ANTHROPOMORPHISM
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% JULIA: there will be 4-5 subsections
%	1) anthropomorphism as a social phenomenon, definitions, origins, etc.
%	2) anthropomorphism as a consequence of anthropomorphic / life-like design
%	3) the link to robotics and HRI, mention the uncanny valley theory ...
%	4) however: we suggest anthropomorphism is more than a static feature ...
%
%

@@

Anthropomorphism is an interesting phenomenon because it tells us something about 
the relationship between the human who anthropomorphizes, and the non-human agent 
which is anthropomorphized. Though commonly observed, it appears controversial, at 
the same time, that humans tend to \textit{``see human in the non-
human''} \citep{epley_seeing_2007}. 
Anthropomorphism as a social phenomenon arises in an interaction 
\citep{persson_anthropomorphism_2000}, and thus includes at least two interaction 
partners: the human and the real or imagined non-human agent. Therefore, one can 
take two main perspectives on explaining anthropomorphism \citep{lee_human_2005}: a human-centered and an artifact-centered. We briefly outline both views in the following. 
It has to be kept in mind that both perspectives are inseparable; they apply at the 
same time, and we would like to present them here just as two different viewpoints 
on the same phenomenon.

By doing so, this section tries to create a common ground in the understanding of 
anthropomorphism, with a focus on the design of robots and human-robot interaction. 
First of all, we would like to propose a clarification of terms.
In short, we propose to use two different terms, in order to differentiate between the human-like design of a non-human agent, and the perception of human-likeness in a non-human agent.
We use the terms \textit{``anthropomorphic design''} and \textit{``anthropomorphic 
form''} interchangeably to refer to an imitation of human form (or in a broader sense 
also animal and natural) in the design of objects and artificial agents. We propose to 
\textit{not} refer to this as \textit{anthropomorphism}.
Because we use \textit{anthropomorphism} to refer to the social phenomenon of 
people's tendency to perceive human-likeness in non human-like agents. This is an important differentiation.

In the following, we first present an artifact-centered perspective on anthropomorphism, and outline how 
the human-like design approach (\textit{anthropomorphic form}) is used in robotics to encourage 
people to interact in a social way with robots. Then, we apply a human-centered 
perspective and shed light on \textit{anthropomorphism as a social phenomenon}. We present 
theories from psychology and cognitive science to explain people's tendency to 
perceive human-like characteristics in non-human agents. In the end, we synthesize 
the presented backgrounds and suggest an extended understanding of anthropomorphism 
as a multi-factor phenomenon.

@@

An artifact-centered perspective explains anthropomorphism from the ascertainable 
parts / the form of the non-human agent, namely the anthropomorphic design of it.
Using the term \textit{``form''} to describe the design of an artifact, we refer 
not only to the shape of an artifact (how the artifact looks like) but to the total 
expression of the product \citep{bartneck_shaping_2004}. \cite{disalvo_hug:_2003} 
argues that \textit{form} includes a product's physical shape, materials, and 
behavioral qualities. Latter aspect is of special importance for interactive 
systems that show some degree of autonomy (independence).
Several categories of anthropomorphic form can be classified, but there is no 
common agreement on the borders and transitions between these categories: 
anthropomorphic, zoomorphic, caricatured, functional \citep{fong_survey_2003}.
The use of nature-inspired and in particular anthropomorphic (human-like) form in the 
design of non-human things is as old and manifold as people's tendency to anthropomorphize. 
Anthropomorphic (and also animal-shaped) forms were used already in prehistoric 
artworks and illustrations, and they have a long-standing tradition in design in 
general, and with respect of the design of daily life things, in particular 
\citep{norman_design_1988,guthrie_bottles_2000}.

>>>>

\title[The Dynamics of Anthropomorphism]{The Dynamics of Anthropomorphism in Human-Robot Interaction}
\author[\firstAuthorLast ]{\Authors}
\address{}
\correspondance{}
\extraAuth{}
\topic{The Uncanny Valley Hypothesis and Beyond}% If your article is part of a Research Topic, please indicate here which.

@@

The Uncanny Valley hypothesis \citep{mori_uncanny_1970} proposes that human-like
designs of objects and non-human agents can evoke both positive and negative feelings 
of affinity in the human observer / user. Positive feelings reflect the experience of 
emotional engagement with and feelings of empathy for the non-human agent
\citep{cheetham_human_2011}. The positive effect of so-called
\textbf{anthropomorphic form} is exploited in the design of artificial agents
(\eg digital characters, robots) for several reasons. Amongst others,
anthropomorphic design should serve to evoke a positive valence as the Uncanny
Valley hypothesis suggests, which in turn should foster people's acceptance of
the artificial agent, and enable effective (human-like and 
human-social) interaction.  However, at a certain point as the non-human agent
approaches but fails to closely resemble a human, the evoked valence in the
human user suddenly turns into a negative uncanny feeling of what
\cite{mori_uncanny_1970} describes as disgust and revulsion. This, in turn,
might lead to rejection of the non-human but human-like agent.  The Uncanny
Valley hypothesis predicts that with further increasing the human-likeness of
the non-human agent such that it appears so realistic that it is not
distinguishable from a human but perceived to be human, the effect is again a
positive one, reflecting feelings and engagement that are similar as those
evoked by a human-human interaction.  Of course, roboticists and developers try
to avoid ``falling'' into this Uncanny Valley with their human-like designs of
artificial agents. Consequently, there is a considerable research effort to
better understand the boundaries of anthropomorphic design and their effects
on the interaction and experience. To date, findings have been however
inconsistent \citep{cheetham_human_2011}.

Along this line, this article aims at fostering a better understanding of
\textbf{anthropomorphism} (noted \Ant in this paper) by considering the phenomenon
as a whole: robotics researchers often tend to believe that
anthropomorphism only describes a static set of human-like features of a robot
(like shape, speech capabilities, facial expressions, etc.). We refer to these
characteristics as the \emph{anthropomorphic design} of the
robot~\citep{fink_anthropomorphism_2012}. But \emph{anthropomorphism} in general
refers to the larger \emph{social phenomenon} that emerges from the (real or
imagined) \emph{interaction} between a robot and a
user~\citep{persson_anthropomorphism_2000}. According to~\cite{epley_when_2008},
this includes for instance emotional states, motivations, intentions
\emph{ascribed by the user} to the robot. As such, the dynamic and
socio-cognitive dimensions of anthropomorphism are essential to understand the
complex bonds that human users build with robots.

@@

To support the reflection, it may be useful to consider a few experimental
results. We studied anthropomorphism in several short- and long-term
human-robot interaction studies that we carried out with embodied robots, both
in ecologically valid real-world environments and controlled lab settings. Those
experiments are presented in details in previously published
articles~\citep{fink_anthropomorphic_2012, fink_living_2013, fink2014which,
lemaignan2014dynamics}. We only highlight here a few qualitative results that
underline the complexity of the phenomenon.

\begin{figure}[h!]
        \centering
        \begin{subfigure}[t]{0.48\columnwidth}
                \includegraphics[width=\textwidth]{roomba-activities.png}
                \caption{Activities related to Roomba, n = 9 households}
                \label{fig:roomba-activities}
        \end{subfigure}%
        \hspace{0.5cm} 
        \begin{subfigure}[t]{0.48\columnwidth}
                \includegraphics[width=\textwidth]{roomba-perception.pdf}
                \caption{People's perception of Roomba, n = 15 participants}
                \label{fig:roomba-perception}
        \end{subfigure}
    \caption{Usage and perception of the Roomba vacuum-cleaning robot over a 6 months period. Qualitative data suggest that people's activities related to the robot as well as their perception of the robot change over time. Overall, a rather low social engagement of the users with the robot, and few perception of human-likeness in the robot were found.}
    \label{fig:roomba}
\end{figure}

Figures~\ref{fig:roomba-activities} and~\ref{fig:roomba-perception} give a first
perspective on how naive users interact and perceive robots over a long period
of time. Here, \emph{Roomba} vacuum cleaning robots were given to nine
households for a 6-months period. The aim was to explore how people use and
perceive the robot over time, and how they generally live with the Roomba in
their home. At various time points, users were asked to rate their perception of
different features of the robot on a 7-point rating scale. As
Figure~\ref{fig:roomba-perception} shows, some features remained stable over
time (\emph{ease of use} and \emph{fun}), and others decreased: the perceived
\emph{usefulness}, \emph{intelligence} and \emph{impact} on their household.
\emph{intelligence} and \emph{impact} reflect the cognitive engagement of the
user towards the machine: we can assume that one does not care to engage in a
(cognitive) interaction with an artifact perceived as non-intelligent and with
no impact on one's life (and the level of activity pictured in
Figure~\ref{fig:roomba-activities} qualitatively confirms this intuition). Even
if one can argue that the Roomba is not designed to foster interaction, it
raises a first question: how to sustain engagement between a robot and a human
over a long period of time? And, as a pre-requisite to answer, do we actually
understand the psychological phenomenon, and can we effectively account for the
dynamics of these interactions?

Those questions are certainly not new, but paradoxically, while anthropomorphism
is a commonly discussed trait of human-robot interaction, it appears
that we lack formal grounds and models that would account for the long-term
dynamics of these interactions.

\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.48\columnwidth}
                \centering
                \includegraphics[width=0.75\textwidth]{ranger}
                \caption{Interaction scenario of the \emph{Ranger} domino study: the robot toy box Ranger transports domino tiles between the two children}
                \label{fig:ranger-expe}
        \end{subfigure}%
        \hspace{0.5cm}
        \begin{subfigure}[b]{0.48\columnwidth}
            \includegraphics[width=\textwidth]{ranger-interactions-vs-qualitative-score}
            \caption{Qualitative level of anthropomorphic projections ($y$-axis) versus the actual interactions with the robot ($x$-axis) are negatively correlated.}
            \label{fig:qualitative-score}
        \end{subfigure}
        \caption{Children`s interactions with the Ranger robot toy box, and their anthropomorphic projections onto the robot. Overall, large variations of both children`s behavior and their perception of the robot were found but seemed to be correlated to each other.}
    \label{fig:ranger}
\end{figure}

%\fixme{It was written as caption of fig:ranger: ``Level of interaction with a semi-anthropomorphic robot is \emph{not} a predictor of anthropomorphic projections.'' Comment JF: this statement does not make sense to me as we found a significant negative correlation between the two.}

Figure~\ref{fig:qualitative-score} calls for other initial remarks. This diagram
shows data from a (yet unpublished) study in which 13 pairs of children (4-5 years old)
played for about 20 minutes a Domino game with a robot toy box (the robot was tasked to
carry domino pieces from one child to the other, Figure~\ref{fig:ranger-expe}).
The $x$-axis represents the number of social interactions between the children
and the robot (like talking to the robot or showing objects), based on video annotations. On
the $y$-axis, we have a synthetic qualitative measurement of anthropomorphic
projections onto the robot, based on two interviews with the children. The correlation between both these
values is significantly \emph{negative}: the more the children engaged into
interaction, the less prone to anthropomorphic projections they were. This
diagram also highlights an interesting cluster of children who did not interact
much with the robot, and still reported a strong anthropomorphic perception of
the robot.

@@

These first remarks lead to the main question we attempt to address in this
article: how can we understand \emph{anthropomorphism} as a whole, \hl{and in such a
way that is support improved human-robot interactions?}\fixme{JF: something's wrong with this sentence}

We propose to discuss anthropomorphism from three
complementary perspectives:

%Based on an extensive literature review~\citep{fink_anthropomorphism_2012},
%several field and lab studies previously mentioned, and insights from the
%cognitive neuroscience, we propose to discuss anthropomorphism from three
%complementary perspectives.

First, by reviewing what anthropomorphism actually \emph{means}:
besides an \emph{artifact-centered} understanding that explains anthropomorphism from the human-like design of the non-human artifact, it seems important to explicit the social component, namely a \emph{human-centered} understanding, of anthropomorphism.

Second, we propose a model, called the \textit{Dynamics of Anthropomorphism} to understand how anthropomorphism evolves over time ~\citep{lemaignan2014dynamics}.
These dynamics are non-monotonic, and effects like the
\emph{novelty effect} play here a key role.

@@

%\paragraph{Two hypotheses}
Our research question also translates to two
hypotheses, which structure the reflections of this article:

\begin{enumerate} 
\item ~A person's tendency to anthropomorphize a robot
    is based on several factors, including (but not limited to) (1) the
    design of the robot, (2) the personal characteristics of the human user,
    and (3) the context and situation of use. For instance, a social context
    and purpose of the robot increase anthropomorphism: \textit{anthropomorphism
    as a multi-factor phenomenon}.

\item ~A person's tendency to anthropomorphize a robot
    evolves in a non-linear way over time and with growing experience that the
    person has with the robot. For instance, a more experienced user will
    perceive the robot as more familiar and predictable, and in turn
    anthropomorphizes the robot less: \textit{anthropomorphism as a dynamic
    phenomenon}.

@@

%\begin{inparaenum}[\itshape 1)\upshape]

The remainder of this article is organized as follows.
According to the three perspectives that we take, 
we first (in Section
%\ref{sec:overview-studies}, we give a brief overview on the various studies that
%we conducted to investigate anthropomorphism, namely \item the Roomba study,
%\item the Forum study, \item the Ranger domino study. Next, Section
\ref{sec:anthropomorphism}) aim to establish a common ground in the
understanding of anthropomorphism. We review literature from several relevant domains and integrate the different explanations into an understanding of
anthropomorphism as a multi-factor phenomenon.
Based on this, Section~\ref{sec:our-ideas} introduces our initial model of the
\textit{Dynamics of Anthropomorphism}. This model describes the variances
and dynamics of people's tendency to anthropomorphize an artificial agent,
such as a robot. 
Then Section \ref{sec:cognition-neuroscience} presents a
cognitive and neuroscience perspective on anthropomorphism to consolidate
our considerations and the proposed model.
This is followed by a discussion
about the limitations of our approach (Section \ref{sec:discussion}) and the
existing and alternative ways to measure anthropomorphism in human-robot
interactions.
Finally, Section \ref{sec:conclusion} concludes this article
and offers starting points for further research on anthropomorphism and the
effect of the human-like design approach in robotics.

%\end{inparaenum}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%		PART 1: WHAT OTHERS DID AND WE ALREADY KNOW ABOUT ANTHROPOMORPHISM
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Anthropomorphism is an interesting phenomenon because it tells us something about 
the relationship between the human who anthropomorphizes, and the non-human agent 
which is anthropomorphized. Though commonly observed, it still appears controversial, at 
the same time, that humans tend to \textit{``see human in the non-
human''} \citep{epley_seeing_2007}. 
To shed light on this phenomenon, first of all, we would like to propose a clarification of terms.
In short, we propose to differentiate between \textbf{anthropomorphic form} to refer to an imitation of human-like form in the \textit{design} of artificial agents, and  \textbf{anthropomorphism} to refer to the social phenomenon of 
people's tendency to \textit{perceive} human-likeness in non human-like agents.
\citep{fink_anthropomorphism_2012} In the following, we might use the terms \texitit{form} and \textit{design} interchangeably.

As anthropomorphism arises in an interaction between a human and a non-human agent
\citep{persson_anthropomorphism_2000}, one can also
take two main perspectives on explaining anthropomorphism \citep{lee_human_2005}: an artifact-centered perspective and a human-centered perspective. 
We now first present an artifact-centered perspective on anthropomorphism, and outline how 
robotics uses \textit{anthropomorphic design} to encourage 
people to interact in a social way with robots.
Then, we present a human-centered 
perspective and shed light on \textit{anthropomorphism as a social phenomenon}. We present 
theories from psychology and cognitive science to explain people's tendency to 
perceive human-like characteristics in non-human agents.
It has to be kept in mind that both perspectives are inseparable; they apply at the 
same time, and we would like to present them here just as two different viewpoints 
on the same phenomenon.
In the end of this section, we synthesize 
the presented backgrounds into an extended understanding of anthropomorphism 
as a multi-factor phenomenon.

@@

An artifact-centered perspective explains anthropomorphism from the ascertainable 
parts of the non-human agent, namely the anthropomorphic form of it.
Using the term \textit{form} to describe the design of an artifact, we refer 
not only to the shape (how it looks like) but to the total 
expression of the artifact \citep{bartneck_shaping_2004}. \cite{disalvo_hug:_2003} 
argues that \textit{form} includes a product's physical shape, materials, and 
behavioral qualities. The behavioral aspect is of special importance for interactive 
systems that show some degree of autonomy (independence).
Several categories of anthropomorphic form can be classified, but there is no 
common agreement on the borders and transitions between these categories: 
anthropomorphic, zoomorphic, caricatured, functional \citep{fong_survey_2003}.
The use of nature-inspired and in particular anthropomorphic (human-like) form in the 
design of non-human things is as old and manifold as people's tendency to anthropomorphize. 
Anthropomorphic (and life-like) forms have a long-standing tradition in design in general, and in the design of daily life things, in particular 
\citep{norman_design_1988,guthrie_bottles_2000}. Interestingly, from its very beginning the image of a robot exists as an outstanding challenge to mankind \citep{replicant_????}. Starting from when the term \texit{robot} first appeared in a play by Karel \^{C}apek in the 1920ies, robots were man-made beings, created as the \textit{``shadow of man''} (and sometimes resembling a human being in appearance).
